Import_Map

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Map edits

PhotoperiodDepthOMZ <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & lat == 45 ~ 0,
                              DayofYear == "Equinox" & DepthNames == "100 m" & lat == 45 ~ 0,
                              DayofYear == "Summer Solstice" & DepthNames == "100 m" & lat == 0  ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                                     DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1))

@@

PhotoperiodDepthFullO2 <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
                                     DayofYear == "Equinox" & lat == 0 ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                               DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                               DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
                               DayofYear == "Equinox" & lat == 0 ~ 0,
                               DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                               DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1))

@@

```{r, Niches figures, fig.height = 10, fig.width = 8, warning = FALSE}
NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw()+
 theme(strip.text = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        plot.margin = unit(c(0,30,0,0), "pt"))

@@

>>>>

PhotoperiodDepthOMZ <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  mutate(DepthNames = factor(DepthNames, levels = c("100 m", "50 m")),
         lat = factor(lat, levels = c("45", "0"))) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & lat == 45 ~ 0,
                              DayofYear == "Equinox" & DepthNames == "100 m" & lat == 45 ~ 0,
                              DayofYear == "Summer Solstice" & DepthNames == "100 m" & lat == 0  ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                                     DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1))

@@

PhotoperiodDepthFullO2 <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  mutate(DepthNames = factor(DepthNames, levels = c("100 m", "50 m")),
         lat = factor(lat, levels = c("45", "0"))) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                              TRUE ~ 1)) |>
  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" ~ 0,
                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
                                     DayofYear == "Equinox" & lat == 0 ~ 0,
                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1 ))  |>
  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
                               DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
                               DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
                               DayofYear == "Equinox" & lat == 0 ~ 0,
                               DayofYear == "Summer Solstice" & lat == 45  ~ 0,
                               DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
                              TRUE ~ 1))

@@

```
#fig.height = 10, fig.width = 8, warning = FALSE
```{r, Niches figures}
NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
         lat = factor(lat, levels = c("45", "0"))) %>%
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    facet_grid(rows = vars(lat),
              cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 3
  )  +
  guides(color = "none") +
  theme_bw()+
 theme(strip.text = element_text(size = 10),
        axis.title = element_blank(),
        # strip.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_blank(),
        axis.ticks.x.bottom = element_blank(),
        axis.ticks.y.left = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        plot.margin = unit(c(0,30,0,0), "pt"))

@@

-------------------------------------------------------------------------------------------------------------------
---------------------------------------------- # SySl changes-----------------------------------------------------------
----------------------------------------------------------------------------------------------------------------

fig.height = 10, fig.width = 6, warning = FALSE
```{r create maps}

map<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        strip.placement = "outside",
        strip.switch.pad.grid = unit(1, "cm"),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
map

map2<-ggplot() + 
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
    # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
    # geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
    # geom_text(data=data_textSummerFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
    # geom_text(data=data_textSummerFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
    # geom_text(data=data_textSummerFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
    # geom_text(data=data_textSummerFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
    #   geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
    #   geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text.x = element_text(size=18, hjust = 0),
        strip.text.y = element_text(size=18),
        axis.title.y = element_text(vjust = -15),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14)) +
  coord_map("moll") 
map2

#fig.height = 10, fig.width = 8, warning = FALSE
   # parse = TRUE,
    hjust = 0,
    vjust = 1,
```{r, Niches figures, fig.height = 4, fig.width = 8, warning = FALSE}

# PhotoperiodDepthFullO2<-PhotoperiodDepthFullO2 %>% 
# PhotoperiodDepthOMZ<-PhotoperiodDepthOMZ %>%

NichesFullO2North <- PhotoperiodDepthFullO2 %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
    facet_grid(cols = vars(DayofYear),
              labeller = labeller(lat = label_both, DayofYear = label_value)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
    size = 6
  )  +
  guides(color = "none") +
  theme_bw()+
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
    facet_grid(cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
    size = 6
  )  +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

NichesOMZNorth <- PhotoperiodDepthOMZ %>%
  filter(lat == 45) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>% 
ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
   labs(title = "Oxygen Minimum Zone") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
    facet_grid(cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
    size = 6
  )  +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

NichesOMZEquat <- PhotoperiodDepthOMZ %>%
  filter(lat == 0) %>% 
mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
        TextLocation = 5) %>%

ggplot()+
  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
            size = 0.5, alpha = 0, show.legend = TRUE)+
  # labs(title = "Full Oxygen") +
  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
    coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
    facet_grid(cols = vars(DayofYear),
              labeller = labeller(lat = label_both)) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
    hjust = 0.5,
    #vjust = 1,
   size = 6)  +
  guides(color = "none") +
  theme_bw() +
  theme(plot.title = element_text(vjust = 10),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        #axis.title = element_text(size=14),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=18),
        #axis.title.y = element_text(vjust = 1),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))

```{r}
P1<-(NichesFullO2North/NichesFullO2Equat)
P1

P2<- (NichesOMZNorth/NichesOMZEquat)
P2

# P3<-P1+FullO2map+P2
# P3

ggarrange(P1, map, P2, ncol = 3, nrow = 1)

# ggarrange(P1, map2, P2, ncol = 3, nrow = 1)

```{r save plot}
ggsave(file = file.path(FigPath, paste("NichesMap_UglySS2",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
```
